---
title: "Team mTurk - Motivating Quality Work"
author: "Kevin Hanna, Kevin Stone, Changjing Zhao"
output:
  html_document: 
    fig_caption: yes
    toc: yes
    toc_depth: 4
---

# Motivating Quality Work
## What motivates crowdsourced workers to do quality work?

Our scoring metric measures the accuracy of the bounding box by calculating the euclidean distance of the Turkers bounds to the correct bounding.
Therefor a **lower score is better**.  When the treatment should cause a negative reaction, the score should increase if our hypothesis is correct.


```{r setup, include=FALSE}
library(data.table)
library(dplyr)
#library(rjson)
library(pwr)
library(stargazer)
library(knitr)
#library(kableExtra)

```

```{r load_data, echo=FALSE}
# Read in all the data, we'll use the 'dataset_no' to pull the results from each experiment. 
d <- fread("./data/experiment_all/experiment_results.csv")

# None of our experiments required creating multiple bounding boxes on a single image.
# We are assuming the extra bounding boxes are mistakes and taking the better score.
remove_extra_bounding_boxes <- function(d) {
  good_scores <- d[,  .(bounding_box_score = min(bounding_box_score), count = .N), keyby=.(WorkerId, ImageId, experiment_no, in_treatment)] %>% .[count<2, ]
  d[good_scores, on=.(WorkerId, ImageId, experiment_no, bounding_box_score, in_treatment)]
}

d <- remove_extra_bounding_boxes(d)

## Create a logical score (so that higher score is better)
max_bounding_box_score <- ceiling(max(d[, bounding_box_score], na.rm=T))
d[, regularized_score := (max_bounding_box_score - bounding_box_score)]


## experiment_no doesn't make sense
d[, dataset_no := experiment_no]

d[dataset_no %in% c(1), experiment := "pilot"]
d[dataset_no %in% c(2), experiment := "social"]
d[dataset_no %in% c(3,4,7), experiment := "future"]
d[dataset_no %in% c(5,6), experiment := "immediate"]

```


```{r formatting_helper_functions, echo=FALSE}

### Change based on rendering being made 

# PDF
#stargazer_type="latex"
# Markdown
stargazer_type="text"
# HTML
#stargazer_type="html"




format_table <- function(table_d, caption = NULL) {
  kable(table_d)
}

```





# Play area, just junk from here

```{r experiment_7_regression, echo=FALSE, results='asis'}
e7_mod_1 <- d[experiment=="future", lm(bounding_box_score ~ in_treatment)]
e7_mod_2 <- d[experiment=="future", lm(bounding_box_score ~ in_treatment+is_cellphone)]
e7_mod_3 <- d[experiment=="future", lm(bounding_box_score ~ in_treatment+factor(mousetrackpad))]
e7_mod_4 <- d[experiment=="future", lm(bounding_box_score ~ in_treatment+factor(Reward))]
e7_mod_5 <- d[experiment=="future", lm(bounding_box_score ~ in_treatment+factor(mousetrackpad)+factor(Reward))]

stargazer(e7_mod_1, e7_mod_2, e7_mod_3,
          type=stargazer_type, header = FALSE, table.placement = 'h', report=('vc*p'),
          add.lines = list(c("Data Subset", "All", "All", "$x==1$")),
          column.labels=c("n=700", "n=700 and cellphone", "n=700 and mousetrackpad"))

```

```{r, echo=FALSE, results='asis'}
stargazer(e7_mod_1, e7_mod_2, e7_mod_3, e7_mod_4,  e7_mod_5,
          type=stargazer_type, header = FALSE, table.placement = 'h', report=('vc*p'),
          add.lines = list(c("Data Subset", "All", "All", "$x==1$")),
          column.labels=c("n=300", "n=300 and cellphone","n=700", "n=700 and cellphone"))
```


```{r, echo=FALSE, results='asis'}

e7_ate = d[dataset_no %in% c(3, 4, 7) & in_treatment == 1, mean(bounding_box_score, na.rm=T)] - d[dataset_no %in% c(3, 4, 7) & in_treatment == 0, mean(bounding_box_score, na.rm=T)]

e7_sd = d[dataset_no %in% c(3, 4, 7), sd(bounding_box_score, na.rm=T)]


power.t.test(delta=abs(e7_ate), 
             sd=e7_sd, 
             sig.level = 0.05,
             power = 0.80,
             alternative = "one.sided",
             n = NULL)
```